% ------ BEGIN PREAMBEL ------
\documentclass[a4paper,10pt, bibliography=totocnumbered]{scrreprt}

\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}

\usepackage{graphicx}
\usepackage{pdfpages}
%\usepackage{subfig}
%\usepackage{microtype}
\usepackage{tabularx}
%\usepackage{amsmath, textcomp}

% Custom packages
\usepackage[numbers]{natbib}
\usepackage{longtable}
\usepackage{ragged2e}
%\usepackage{tikz}
%\usetikzlibrary{positioning}
%\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{textgreek}

\usepackage{csquotes}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{tablefootnote}
\usepackage{float}

% Links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,        % color of internal links
%    citecolor=green,        % color of links to bibliography
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}

% Glossary
\usepackage[nomain,acronym,toc]{glossaries} 
\makeglossaries
\input{./content/glossary}

% ------ BEGIN EDINGER PACKAGES ------
\usepackage{xcolor}
\usepackage{array}
\usepackage{booktabs}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\usepackage{multirow}
\usepackage{pdflscape}
\usepackage[pass]{geometry} % Für Landscapes

% define colors and configure listing
\colorlet{mygray}{black!30}
\colorlet{mygreen}{green!60!blue}
\colorlet{mymauve}{red!60!blue}
\lstset { %
	language=C++,
	backgroundcolor=\color{gray!10},  
	basicstyle=\ttfamily,
	columns=fullflexible,
	breakatwhitespace=false,      
	breaklines=true,                
	captionpos=t,                    
	commentstyle=\color{mygreen},
	emph={aspect, advice, pointcut, before, JoinPoint, UC, context, pre, @pre, post, and, or, not, implies, forall, exists, String, Contract, Scalar, Observability, Responsibility, Metric, Reports, Exports, Scenario}, emphstyle={\color{blue}},
	extendedchars=true,              
	frame=single,                   
	keepspaces=true,             
	keywordstyle=\color{blue},      
	language=c++,                 
	numbers=none,                
	numbersep=5pt,                   
	numberstyle=\tiny\color{blue}, 
	rulecolor=\color{mygray},        
	showspaces=false,               
	showtabs=false,                 
	stepnumber=1,                  
	stringstyle=\color{mymauve},    
	tabsize=3,                      
	title=\lstname,
	numbers=left
}
% ------ END EDINGER PACKAGES ------

% ------ BEGIN HAUSBERGER PACKAGES ------
%\usepackage{csquotes}
%\usepackage{float}
% \usepackage{color}

% \definecolor{dkgreen}{rgb}{0,0.6,0}
% \definecolor{gray}{rgb}{0.5,0.5,0.5}
% \definecolor{mauve}{rgb}{0.58,0,0.82}

%\lstset{
%	frame=tb,
%	language=Java,
%	aboveskip=3mm,
%	belowskip=3mm,
%	showstringspaces=false,
%	columns=flexible,
%	basicstyle={\small\ttfamily},
%	morekeywords={UC, context, pre, @pre, post, and, or, not, implies, forall, exists},
%	numbers=none,
%	numberstyle=\tiny\color{gray},
%	keywordstyle=\color{blue},
%	commentstyle=\color{dkgreen},
%	stringstyle=\color{mauve},
%	breaklines=true,
%	breakatwhitespace=true,
%	tabsize=3
%}
% ------ END HAUSBERGER PACKAGES ------

% ------ BEGIN KOCH PACKAGES ------
% Auskommentiert: Wir nutzen utf8; \usepackage[latin1]{inputenc}
% \usepackage[a4paper]{geometry}
% \geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2.5cm,rmargin=2.5cm}
% \setcounter{secnumdepth}{3}
% \setcounter{tocdepth}{3}
% \usepackage{babel}
% \usepackage{array}
% \usepackage{longtable}
% \usepackage{float}
% \usepackage{textcomp}
% \usepackage{graphicx}
% \usepackage[unicode=true,
%  bookmarks=false,
%  breaklinks=false,pdfborder={0 0 1},backref=section,colorlinks=false]
%  {hyperref}
% \hypersetup{pdftitle={Titel},
%  pdfauthor={Autor},
%  pdfpagelabels=true}
 
 % ------ END KOCH PACKAGES ------


% ------ BEGIN YAGMUR ARSLAN - TOPIC7 PACKAGES ------
%\usepackage{multirow}
%\usepackage{array}
%\usepackage{float}
%\usepackage{tablefootnote}
%\usepackage[pass]{geometry}
%\usepackage{pdflscape}
\usepackage{lscape}
\usepackage{chngpage}
\usepackage{afterpage}
%\restylefloat{table}
\usepackage{enumitem}

% ------ END YAGMUR ARSLAN - TOPIC7 PACKAGES ------


% ------ END PREAMBEL ------

%% Title Page
\makeatletter
\renewcommand{\maketitle}{\begin{titlepage}
    \vskip 10\p@
    \hbox{
      \vrule depth 0.99\textheight
        \mbox{\hspace{2em}}
      \vtop{
        \vskip 10\p@
        \hspace{4pt}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@author \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \huge \bfseries \@title \par
        \end{flushleft}
        \begin{flushleft}
          \Large \bfseries \@subtitle \par
        \end{flushleft}
        \vskip 70\p@
        \begin{flushleft}
          \Large \@publishers \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@date \par
        \end{flushleft}
        }}
  \end{titlepage}
}
\makeatother

\author{Yagmur Arslan, Max Edinger, Ahmet Efe, Julian Gröger, Felix Hausberger, Stefan Hickl, Tobias Koch, Jasmin Mangei, Andre Meyering}
\title{Better software through systematic testing }
%\subtitle{}
\publishers{\textbf{Advisor University of Heidelberg}\\ Prof. Dr. Barbara Paech, Astrid Rohmann}
\date{February 26, 2021}



% Deutsche Absaetze:
\parindent 0pt
\parskip 12pt

\textwidth145mm
\setlength{\oddsidemargin}{0.7cm}
\setlength{\topmargin}{-0.5cm}
\setlength{\textheight}{22.5cm}

\begin{document}
\maketitle

\include{./content/0-Abstract}

\tableofcontents

\input{./content/1-Introduction}
\input{./content/02-Topic-1}
\input{./content/03-Topic-2}
\input{./content/04-Topic-3}
\input{./content/05-Topic-4}
\input{./content/06-Topic-5}
\input{./content/07-Topic-6}
\input{./content/08-Topic-7}
\input{./content/09-Topic-8}
\input{./content/10-Topic-9}
\input{./content/11-Topic-10}
\input{./content/12-Conclusion}

%% Glossary
\glsaddall
\printglossary[title={Glossary},nonumberlist]

%% Bibliography
\bibliographystyle{plainnat}
%\bibliography{literature.bib}%Bibliography file name

\begin{thebibliography}{9}

\bibitem{KunChen2005} Chen, K., Zhang, W., Zhao, H.: "An approach to constructing feature models based on requirements clustering," 13th IEEE International Conference on Requirements Engineering (RE'05), Paris, 2005, pp. 31-40, doi: 10.1109/RE.2005.9.

\bibitem{RichtigesZitierenTUDresden} Institut für Geographie   
Lehrstuhl für Allgemeine Wirtschafts- und Sozialgeographie: An Hinweise zum wissenschaftlichen Arbeiten.
\url{http://www.geogr.uni-jena.de/fileadmin/Geoinformatik/Lehre/backup_05_2007/pdf-dokumente/Skript_WissArbeiten.pdf}

\bibitem{SWEBOK} Bourque, P., Fairley, R. E.: Guide to the Software Engineering Body of Knowledge. Version 3.0.
IEEE Computer Society, 2014. \url{https://cs.fit.edu/~kgallagher/Schtick/Serious/SWEBOKv3.pdf}, last accessed 2021/02/06.

% https://ieeexplore.ieee.org/document/4578345/references#references
\bibitem{ZouPavlovski2008} Zou, J., Pavlovski C. J.: "Control Cases during the Software Development Life-Cycle," 2008 IEEE Congress on Services - Part I, Honolulu, HI, 2008, pp. 337-344, doi: 10.1109/SERVICES-1.2008.46.

% https://ieeexplore.ieee.org/abstract/document/6908675
\bibitem{Lagerstedt2014} Lagerstedt, R.: "Using automated tests for communicating and verifying non-functional requirements," 2014 IEEE 1st International Workshop on Requirements Engineering and Testing (RET), Karlskrona, 2014, pp. 26-28, doi: 10.1109/RET.2014.6908675.

% https://ieeexplore.ieee.org/document/1438375
\bibitem{Andre_Search_1} Gregoriades, A., Sutcliffe, A.: "Scenario-based assessment of nonfunctional requirements," in IEEE Transactions on Software Engineering, vol. 31, no. 5, pp. 392-409, May 2005, doi: 10.1109/TSE.2005.59.

% https://ieeexplore.ieee.org/document/5954452
\bibitem{Andre_Search_2} Barmi, Z. A., Ebrahimi, A. H., Feldt, R.: "Alignment of Requirements Specification and Testing: A Systematic Mapping Study," 2011 IEEE Fourth International Conference on Software Testing, Verification and Validation Workshops, Berlin, 2011, pp. 476-485, doi: 10.1109/ICSTW.2011.58.

\bibitem{el-attar} El-Attar, M., Miller, J.: Developing comprehensive acceptance tests from use cases and robustness diagrams. Requirements Eng 15, 2010, pp. 285–306, \url{https://doi.org/10.1007/s00766-009-0088-6}

\bibitem{longo} Longo, D., Vilain, P.: Pereira da Silva, L., Mello, R.: 2016. A web framework for test automation: user scenarios through user interaction diagrams. In Proceedings of the 18th International Conference on Information Integration and Web-based Applications and Services (iiWAS '16). Association for Computing Machinery, New York, NY, USA, 458–467. doi: \url{https://doi.org/10.1145/3011141.3011158}

\bibitem{longo2} Longo, D.H. and Vilain, P.: "Creating User Scenarios through User Interaction Diagrams by Non-Technical Customers." In SEKE, 2015, pp. 330-335, doi: 10.18293/SEKE2015-179.

\bibitem{acm} ACM Digital Library. \url{https://dl.acm.org/} 

\bibitem{fitnesse} FitNesse. \url{http://docs.fitnesse.org/FrontPage}, last accessed 2021/02/06.

\bibitem{ieee} IEEE Xplore. \url{https://ieeexplore.ieee.org/Xplore/home.jsp}, last accessed 2021/02/06.

\bibitem{springer} Springer Link. \url{https://link.springer.com/}, last accessed 2021/02/06.

\bibitem{elsevier} Science Direct. \url{https://www.sciencedirect.com/}, last accessed 2021/02/06.

\bibitem{Fit-tables} FitNesse: Writing Fit Tables. \url{http://fitnesse.org/FitNesse.UserGuide.WritingAcceptanceTests.FitFramework.WritingFitTables}, last accessed 2021/02/06.

% ------ BEGIN REFERENCES HAUSBERGER ------ 

\bibitem{ClementineNebut2006} Nebut, C., Fleurey, F., Le Traon, Y., Jézéquel, J.-M.: "Automatic test generation: a use case driven approach," in IEEE Transactions on Software Engineering, vol. 32, no. 3, pp. 140-155, March 2006, doi: 10.1109/TSE.2006.22.

\bibitem{NajlaRaza2007} Raza, N., Nadeem, A., Iqbal, M. Z. Z.: "An Automated Approach to System Testing Based on Scenarios and Operations Contracts," Seventh International Conference on Quality Software (QSIC 2007), Portland, OR, 2007, pp. 256-261, doi: 10.1109/QSIC.2007.4385504

\bibitem{FelixHausberger2020} Hausberger, F.: Research planning, research and mid-term presentation, \url{https://github.com/fidsusj/SWE-Seminar}, last accessed 2021/01/10.

\bibitem{MonalisaSarma2007} Sarma, M., Mall, R.: "System Testing using UML Models," 16th Asian Test Symposium (ATS 2007), Beijing, 2007, pp. 155-158, doi: 10.1109/ATS.2007.102.

\bibitem{RosziatiIbrahim2007} Ibrahim, R., Saringat, M. Z., Ibrahim, N., Ismail, N.: "An Automatic Tool for Generating Test Cases from the System's Requirements," 7th IEEE International Conference on Computer and Information Technology (CIT 2007), Aizu-Wakamatsu, Fukushima, 2007, pp. 861-866, doi: 10.1109/CIT.2007.116.


\bibitem{LizheChen2010} Chen, L., Li, Q.: "Automated test case generation from use case: A model based approach," 2010 3rd International Conference on Computer Science and Information Technology, Chengdu, 2010, pp. 372-377, doi: 10.1109/ICCSIT.2010.5563772.

\bibitem{XiaojingZhang2015} Zhang, X., Tanno, H.: "Requirements document based test scenario generation for web application scenario testing," 2015 IEEE Eighth International Conference on Software Testing, Verification and Validation Workshops (ICSTW), Graz, 2015, pp. 1-3, doi: 10.1109/ICSTW.2015.7107465.

\bibitem{LipingLi2008} Li, L., Miao, H.: "An Approach to Modeling and Testing Web Applications Based on Use Cases," 2008 International Symposium on Information Science and Engineering, Shanghai, 2008, pp. 506-510, doi: 10.1109/ISISE.2008.265.

\bibitem{YGKim1999} Kim, Y. G., Hong, H. S., Cho, S. M., Bae, D. H., Cha, S. D.: Test cases generation from UML state diagrams.
In: IEEE Proceedings - Software, Vol. 146, No. 4, pp. 187-192, Aug. 1999.
https://doi.org/10.1049/ip-sen:19990602.

\bibitem{ClementineNebut2003} Nebut, C., Fleurey, F., Le Traon, Y., Jézéquel, J.-M.: 2003. Requirements by Contracts allow Automated System Testing. In Proceedings of the 14th International Symposium on Software Reliability Engineering (ISSRE '03). IEEE Computer Society, USA, 85.
https://dl.acm.org/doi/10.5555/951952.952350.

% Glossary

\bibitem{Kiczales1997} Kiczales, G., Lamping, J., Mendhekar, A., Maeda, C., Lopes, C., Loingtier, J. M., Irwin, J.: (1997) Aspect-oriented programming. In: Akşit M., Matsuoka S. (eds) ECOOP'97 — Object-Oriented Programming. ECOOP 1997. Lecture Notes in Computer Science, vol 1241. Springer, Berlin, Heidelberg.
https://doi.org/10.1007/BFb0053381

\bibitem{Heinz2010} Heinz, J., Koch, D.: Antiblockiersystem ABS.
In: Reif K. (eds) Fahrstabilisierungssysteme und Fahrerassistenzsysteme (2010). Vieweg+Teubner. 
https://doi.org/10.1007/978-3-8348-9717-6\_3

\bibitem{Conrad2005} Conrad, M., Fey, I., Sadeghipour, S.: Systematic Model-Based Testing of Embedded Automotive Software. 
In: Electronic Notes in Theoretical Computer Science 111, 2005.
https://doi.org/10.1016/j.entcs.2004.12.005

\bibitem{Ammann2021} Ammann, P., Offutt, J.: Introduction to Softwate Testing Chapter 3.1, 3.2 Logic Coverage, \url{https://www.cs.montana.edu/courses/se422/currentLectures/Ch3-1-2.pdf}, last accessed 2021/01/28.

\bibitem{Fowler2010} Fowler, M., Parsons, R.: Domain Specific Languages
Addison-Wesley Professional, 2010.

\bibitem{Belli2009} Belli, F., Hollmann, A.: "A Graph-Model-Based Testing Method Compared with the Classification Tree Method for Test Case Generation," 2009 Third IEEE International Conference on Secure Software Integration and Reliability Improvement, Shanghai, 2009, pp. 193-200, doi: 10.1109/SSIRI.2009.40.

\bibitem{Amyot2011} Amyot, D., Mussbacher, G.: User Requirements Notation: The First Ten Years, The Next Ten Years (Invited Paper). 
In: Journal of Software 6(5):747-768 (2011). 
https://doi.org/10.4304/jsw.6.5.747-768

\bibitem{ETSI2021} ETSI: Testing, Interoperability and Technical Quality, \url{https://portal.etsi.org/CTI/CTISupport/Glossary.htm}, last accessed 2021/02/01.

\bibitem{JUnit4} JUnit: JUnit, \url{https://junit.org/junit4/}, last accessed 2021/02/01.

\bibitem{OCL} Object Management Group: Object Constraint Language, \url{https://www.omg.org/spec/OCL/2.4/PDF}, last accessed 2021/02/01.

\bibitem{Stakeholders} Software Testing Class: Involvement Of Stakeholders In Testing, \url{https://www.softwaretestingclass.com/involvement-of-stakeholders-in-testing/}, last accessed 2021/02/01.

\bibitem{SysML} SysML: SysML Open Source Project - What is SysML? Who created SysML?, \url{https://sysml.org/}, last accessed 2021/02/01.

\bibitem{STFTestCase} Software Testing Fundamentals: Test Case, \url{https://softwaretestingfundamentals.com/test-case/}, last accessed 2021/02/01.

\bibitem{AOTTestScenario} Art Of Testing: Test Scenario, \url{https://artoftesting.com/test-scenario-examples}, last accessed 2021/02/01.

\bibitem{UML} UML Diagrams: The Unified Modeling Language, \url{https://www.uml-diagrams.org/}, last accessed 2021/02/01.


% ------ END REFERENCES HAUSBERGER ------ 

% ------ BEGIN REFERENCES EDINGER ------ 

\bibitem{C++} AspectC++ Development Team: About the Project.
\url{https://www.aspectc.org/}, last accessed 2020/12/28.

\bibitem{Dijkstra} Dijkstra, E.: A Discipline of Programming.
In: Prentice-Hall Series in Automatic Computation Englewood Cliffs, New Jersey, 1976.

\bibitem{Duclos} Duclos, E., Le Digabel, S., Guéhéneuc, Y.,  Adams, B.: "ACRE: An Automated Aspect Creator for Testing C++ Applications," 2013 17th European Conference on Software Maintenance and Reengineering, Genova, 2013, pp. 121-130, doi: 10.1109/CSMR.2013.22.

\bibitem{J} Eclipse Foundation: AspectJ.
\url{https://www.eclipse.org/aspectj/},  last accessed 2020/12/28.

\bibitem{Metsa} Metsä, J., Katara, M., Mikkonen, T.: "Testing Non-Functional Requirements with Aspects: An Industrial Case Study," Seventh International Conference on Quality Software (QSIC 2007), Portland, OR, 2007, pp. 5-14, doi: 10.1109/QSIC.2007.4385475.

\bibitem{Parnas} Parnas, D.: On the criteria to be used in decomposing systems into modules.
In: Communications of the ACM, 1972.

% ------ END REFERENCES EDINGER ------ 


% ------ BEGIN REFERENCES KOCH ------
\bibitem{Siegl2010} Siegl, S., Hielscher K.-S., German R.: "Model Based Requirements Analysis and Testing of Automotive Systems with Timed Usage Models," 2010 18th IEEE International Requirements Engineering Conference, Sydney, NSW, 2010, pp. 345-350, doi: 10.1109/RE.2010.49.

\bibitem{Guan2015} Guan, J., Offutt, J.: "A model-based testing technique for component-based real-time embedded systems," 2015 IEEE Eighth International Conference on Software Testing, Verification and Validation Workshops (ICSTW), Graz, 2015, pp. 1-10, doi: 10.1109/ICSTW.2015.7107407.

\bibitem{imdb} IMDB. \url{https://www.imdb.com/}, last accessed 2021/02/06.

% ------ END REFERENCES KOCH ------



% ------ BEGIN REFERENCES YAGMUR ARSLAN -TOPIC 7 ------
\bibitem{Paper1} Abbors F., Truscan D., Lilius J.: "Tracing Requirements in a Model-Based Testing Approach," 2009 First International Conference on Advances in System Testing and Validation Lifecycle, Porto, 2009, pp. 123-128, doi: 10.1109/VALID.2009.15.

\bibitem{matera} Abbors F., Bäcklund A., Truscan D.: "MATERA - An Integrated Framework for Model-Based Testing," 2010 17th IEEE International Conference and Workshops on Engineering of Computer Based Systems, Oxford, 2010, pp. 321-328, doi: 10.1109/ECBS.2010.46.

\bibitem{SMvsTM} Malik Q. A., et al.: "Model-Based Testing Using System vs. Test Models - What Is the Difference?," 2010 17th IEEE International Conference and Workshops on Engineering of Computer Based Systems, Oxford, 2010, pp. 291-299, doi: 10.1109/ECBS.2010.41.

\bibitem{Paper2} Bernard E., Legeard B.: "Requirements Traceability in the Model-Based Testing Process,"  in Software Engineering, ser. Lecture Notes in Informatics, vol. 106. Bttinger, Stefan and Theuvsen, Ludwig and Rank, Susanne and Morgenstern, Marlies, 2007, pp. 45–54, ISSN: 1617-5468

\bibitem{LRGuidelines} Chair of Software Engineering of University Heidelberg. Guidelines for literature research.
\url{https://confluence-se.ifi.uni-heidelberg.de/x/XQAyDg}, last accessed 2021/02/06. 

\bibitem{Relevant3} Bouquet F. , Grandpierre C., Legeard B., Peureux F., Vacelet N., Utting M.: 2007. A subset of precise UML for model-based testing. In Proceedings of the 3rd international workshop on Advances in model-based testing (A-MOST '07). Association for Computing Machinery, New York, NY, USA, 95–104. doi: https://doi.org/10.1145/1291535.1291545

\bibitem{Relevant4} Bouquet F., Jaffuel E., Legeard B., Peureux F., Utting M.: 2005. Requirements traceability in automated test generation: application to smart card software validation. SIGSOFT Softw. Eng. Notes 30, 4 (July 2005), 1–7. doi: https://doi.org/10.1145/1082983.1083282

\bibitem{MovieManager} Chair of Software Engineering of University Heidelberg. Movie Manager Example. 
\url{https://confluence-se.ifi.uni-heidelberg.de/x/IgC6Dg}, last accessed 2021/02/06. 

\bibitem{netreqdia} t2informatik GmbH. Requirement Diagram.
\url{https://t2informatik.de/en/smartpedia/requirement-diagram/}, last accessed 2021/02/06. 

\bibitem{traqml} Malik Q. A., Truscan D., Lilius J.: "Using UML Models and Formal Verification in Model-Based Testing," 2010 17th IEEE International Conference and Workshops on Engineering of Computer Based Systems, Oxford, 2010, pp. 50-56, doi: 10.1109/ECBS.2010.13.

\bibitem{LTG} Bernard, E., Bouquet, F., Charbonnier, A., Legeard, B., Peureux, F., Utting, M., Torreborre, E.: 2006. Model-based testing from UML models. In: Hochberger, C. \& Liskowsky, R. (Hrsg.), INFORMATIK 2006 – Informatik für Menschen – Band 2, Beiträge der 36. Jahrestagung der Gesellschaft für Informatik e.V. (GI). Bonn: Gesellschaft für Informatik e.V. (S. 223-230),  ISSN: 1617-5468.

% ------ END REFERENCES YAGMUR ARSLAN -TOPIC 7 ------



% ------ BEGIN REFERENCES Ahmet Efe -TOPIC 8 ------

\bibitem{ArnoldCorriveauShi2010} Arnold, D., Corriveau, J.-P., and Shi, W.: "Scenario-Based Validation: Beyond the User Requirements Notation," 2010 21st Australian Software Engineering Conference, Auckland, 2010, pp. 75-84, doi: 10.1109/ASWEC.2010.29.

\bibitem{BoucherMussbacher2017} Boucher, M., Mussbacher, G.: "Transforming Workflow Models into Automated End-to-End Acceptance Test Cases," 2017 IEEE/ACM 9th International Workshop on Modelling in Software Engineering (MiSE), Buenos Aires, 2017, pp. 68-74, doi: 10.1109/MiSE.2017.5.

% ------ END REFERENCES Ahmet Efe -TOPIC 8 ------

% ------ BEGIN REFERENCES Julian Gröger -TOPIC 5 ------

\bibitem{Belli}
Belli, F., Hollmann, A.: "A Graph-Model-Based Testing Method Compared with the Classification Tree Method for Test Case Generation," 2009 Third IEEE International Conference on Secure Software Integration and Reliability Improvement, Shanghai, 2009, pp. 193-200, doi: 10.1109/SSIRI.2009.40.

\bibitem{Conrad}
Conrad, M., Fey, I., Sadeghipour, S.: "Systematic Model-Based Testing of Embedded
Automotive Software," Electronic Notes in Theoretical Computer Science, Volume 111, 2005, pp. 13-26, ISSN: 1571-0661, doi: \url{https://doi.org/10.1016/j.entcs.2004.12.005}.

% ------ END REFERENCES Julian Gröger -TOPIC 5 ------

\end{thebibliography}

\listoffigures

\listoftables

\end{document}          
