\chapter{Glossary} \label{glossary}

\textbf{Contract.} A requirement-level logical expression used to express preconditions and postconditions of an \textit{operation}.

\textbf{Coverage criterion.} A criterion used to limit the amount of \textit{test objectives} to be generated. Specifies which paths to traverse in the context of the traversal of a \textit{transition system}. 

\textbf{Interaction Overview Diagram (IOD).} A special form of activity diagram used to show control flow. Each node in the IOD represents either an interaction diagram (sequence diagrams) or interaction occurrences that show an \textit{operation} invocation.

\textbf{Object Constraint Language (OCL).} A declarative language in the UML standard used to define \textit{contracts}. 

\textbf{Operation.} An abstract term used to describe a state transition in a \textit{transition system}. Is equal to a \textit{use case} in \cite{ClementineNebut2006} or to an interaction diagram/interaction occurrence in \cite{NajlaRaza2007}.

\textbf{Test case.} Tests a single \textit{use case}.

\textbf{Test objective.} A synonym for test path as a combination of abstract \textit{operations} to be composed into one \textit{test scenario}. 

\textbf{Test scenario.} A sequential composition of \textit{test cases}.

\textbf{Transition system.} Used to derive \textit{test scenarios} by helping to generate \textit{test objectives} through its traversal. Consists of states and transitions, where states are given by \textit{contracts} and transitions are given by \textit{operations}. 

\textbf{UC-System.} A prototype/interpreter-tool used to build a \textit{transition system} in \cite{ClementineNebut2006} and to derive \textit{test objectives} from it. 

\textbf{UC-SCSystem.} A prototype-tool using \textit{use case scenarios} to derive executable \textit{test scenarios} as JUnit tests in \cite{ClementineNebut2006}. 

\textbf{Use case.} An abstract, requirement-level term used to describe a main functionality of a system.

\textbf{Use case scenario.} A synonym for sequence diagram in case of \cite{ClementineNebut2006}.

\textbf{XML Metadata Interchange (XMI).} XML based metadata interchange format gained from an \textit{Interaction Overview Diagram} in \cite{NajlaRaza2007} to generate a \textit{transition system}.
