\documentclass[a4paper,10pt, bibliography=totocnumbered]{scrreprt}

\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}

\usepackage{graphicx}
\usepackage{pdfpages}
%\usepackage{subfig}
%\usepackage{microtype}
\usepackage{tabularx}
%\usepackage{amsmath, textcomp}

% Custom packages
\usepackage[numbers]{natbib}
\usepackage{longtable}
\usepackage{ragged2e}
%\usepackage{tikz}
%\usetikzlibrary{positioning}
%\usepackage{pdflscape}
%\usepackage{rotating}

%--------------------------------------------------------------------
%Efe
\usepackage{multirow}
\usepackage{pdflscape}
\usepackage[pass]{geometry}
\usepackage{listings}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.9,0.9,0.9}
\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{blue},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=8pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}
\lstset{style=mystyle,
	escapechar=¢,
	language=java,
	frame=single,
	rulecolor=\color{black},
	xleftmargin=.026\textwidth, 
	xrightmargin=.018\textwidth
}
%--------------------------------------------------------------------

\usepackage{glossaries} 

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,        % color of internal links
%    citecolor=green,        % color of links to bibliography
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}


%% Title Page
\makeatletter
\renewcommand{\maketitle}{\begin{titlepage}
    \vskip 10\p@
    \hbox{
      \vrule depth 0.99\textheight
        \mbox{\hspace{2em}}
      \vtop{
        \vskip 10\p@
        \hspace{4pt}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@author \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \huge \bfseries \@title \par
        \end{flushleft}
        \begin{flushleft}
          \Large \bfseries \@subtitle \par
        \end{flushleft}
        \vskip 70\p@
        \begin{flushleft}
          \Large \@publishers \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@date \par
        \end{flushleft}
        }}
  \end{titlepage}
}
\makeatother

\author{Author 1, Author n}
\title{Title }
\subtitle{Technical Report}
\publishers{\textbf{Advisor University of Heidelberg}\\ Prof. Dr. Barbara Paech, Astrid Rohmann}
\date{mm dd, year}



% Deutsche Absaetze:
\parindent 0pt
\parskip 12pt

\textwidth145mm
\setlength{\oddsidemargin}{0.7cm}
\setlength{\topmargin}{-0.5cm}
\setlength{\textheight}{22.5cm}

\begin{document}
\maketitle

\include{./content/0-Abstract}

\tableofcontents

\input{./content/1-Introduction}
\input{./content/2-Chapter2}
\input{./content/3-Chapter3}
\input{./content/9-URN}
\input{./content/10-Conclusion}

%% Bibliography
\bibliographystyle{plainnat}
%\bibliography{literature.bib}%Bibliography file name

\begin{thebibliography}{9}

\bibitem{KunChen2005} Chen, K, Zhang, W., Zhao, H.: An approach to constructing feature models based on requirements clustering.
In: 13th IEEE International Conference on Requirements Engineering (RE05). pp. 31-40. (2005)

\bibitem{RichtigesZitierenTUDresden} Institut für Geographie   
Lehrstuhl für Allgemeine Wirtschafts- und Sozialgeographie: An Hinweise zum wissenschaftlichen Arbeiten.
\url{http://www.geogr.uni-jena.de/fileadmin/Geoinformatik/Lehre/backup_05_2007/pdf-dokumente/Skript_WissArbeiten.pdf}

\bibitem{ArnoldCorriveauShi2010} Arnold, D., Corriveau, J.-P., and Shi, W., Scenario-Based Validation: Beyond the User Requirements Notation, 21st Australian Software Engineering Conf. (ASWEC 2010), IEEE CS, pp. 75–84, 2010. DOI:10.1109/ASWEC.2010.29.

\bibitem{BoucherMussbacher2017} Boucher, M., Mussbacher, G.: Transforming Workflow Models into Automated End-to-End Acceptance Test Cases, Proc. - 2017 IEEE/ACM 9th International Workshop on Modelling in Software Engineering. MiSE 2017, pp. 68–74, 2017. DOI:10.1109/MiSE.2017.5.

\end{thebibliography}

\listoffigures

\listoftables

\end{document}          
