\documentclass[a4paper,10pt, bibliography=totocnumbered]{scrreprt}

\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}

\usepackage{graphicx}
\usepackage{pdfpages}
%\usepackage{subfig}
%\usepackage{microtype}
\usepackage{tabularx}
%\usepackage{amsmath, textcomp}

% Custom packages
\usepackage[numbers]{natbib}
\usepackage{longtable}
\usepackage{ragged2e}
%\usepackage{tikz}
%\usetikzlibrary{positioning}
%\usepackage{pdflscape}
%\usepackage{rotating}

\usepackage{glossaries} 

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,        % color of internal links
%    citecolor=green,        % color of links to bibliography
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}

% packages Max Edinger
\usepackage{listings}
\usepackage{xcolor}
\usepackage{array}
\usepackage{booktabs}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\usepackage{multirow}
\usepackage{pdflscape}
\usepackage[pass]{geometry}


% define colors and configure listing
\colorlet{mygray}{black!30}
\colorlet{mygreen}{green!60!blue}
\colorlet{mymauve}{red!60!blue}
\lstset { %
    language=C++,
    backgroundcolor=\color{gray!10},  
    basicstyle=\ttfamily,
    columns=fullflexible,
    breakatwhitespace=false,      
    breaklines=true,                
    captionpos=t,                    
    commentstyle=\color{mygreen},
    emph={aspect, advice, pointcut, before, JoinPoint}, emphstyle={\color{blue}},
    extendedchars=true,              
    frame=single,                   
    keepspaces=true,             
    keywordstyle=\color{blue},      
    language=c++,                 
    numbers=none,                
    numbersep=5pt,                   
    numberstyle=\tiny\color{blue}, 
    rulecolor=\color{mygray},        
    showspaces=false,               
    showtabs=false,                 
    stepnumber=1,                  
    stringstyle=\color{mymauve},    
    tabsize=3,                      
    title=\lstname,
    numbers=left
}

%% Title Page
\makeatletter
\renewcommand{\maketitle}{\begin{titlepage}
    \vskip 10\p@
    \hbox{
      \vrule depth 0.99\textheight
        \mbox{\hspace{2em}}
      \vtop{
        \vskip 10\p@
        \hspace{4pt}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@author \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \huge \bfseries \@title \par
        \end{flushleft}
        \begin{flushleft}
          \Large \bfseries \@subtitle \par
        \end{flushleft}
        \vskip 70\p@
        \begin{flushleft}
          \Large \@publishers \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@date \par
        \end{flushleft}
        }}
  \end{titlepage}
}
\makeatother

\author{Author 1, Author n}
\title{Title }
\subtitle{Technical Report}
\publishers{\textbf{Advisor University of Heidelberg}\\ Prof. Dr. Barbara Paech, Astrid Rohmann}
\date{mm dd, year}



% Deutsche Absaetze:
\parindent 0pt
\parskip 12pt

\textwidth145mm
\setlength{\oddsidemargin}{0.7cm}
\setlength{\topmargin}{-0.5cm}
\setlength{\textheight}{22.5cm}

\begin{document}
\maketitle

\include{./content/0-Abstract}

\tableofcontents

\input{./content/1-Introduction}
\input{./content/2-Chapter2}
\input{./content/3-Chapter3}
\input{./content/11-Chapter11}
\input{./content/10-Conclusion}

%% Bibliography
\bibliographystyle{plainnat}
%\bibliography{literature.bib}%Bibliography file name

\begin{thebibliography}{9}

\bibitem{C++} AspectC++ Development Team: About the Project.
\url{https://www.aspectc.org/} last accessed 2020/12/28

\bibitem{KunChen2005} Chen, K, Zhang, W., Zhao, H.: An approach to constructing feature models based on requirements clustering.
In: 13th IEEE International Conference on Requirements Engineering (RE05). pp. 31-40. (2005)

\bibitem{Dijkstra} Dijkstra, E.: A Discipline of Programming.
In: Prentice-Hall Series in Automatic Computation Englewood Cliffs, New Jersey. (1976)

\bibitem{Duclos} Duclos, E., Le Digabel, S., Guéhéneuc, Y.,  Adams, B.: "ACRE: An Automated Aspect Creator for Testing C++ Applications“.
In:  CSMR 2013 Genova.  pp. 121-130. (2013). \url{10.1109/CSMR.2013.22}

\bibitem{J} Eclipse Foundation: AspectJ.
\url{https://www.eclipse.org/aspectj/}  last accessed 2020/12/28

\bibitem{RichtigesZitierenTUDresden} Institut für Geographie   
Lehrstuhl für Allgemeine Wirtschafts- und Sozialgeographie: An Hinweise zum wissenschaftlichen Arbeiten.
\url{http://www.geogr.uni-jena.de/fileadmin/Geoinformatik/Lehre/backup_05_2007/pdf-dokumente/Skript_WissArbeiten.pdf}

\bibitem{Metsa} Metsä, J., Katara, M., Mikkonen, T.: "Testing Non-Functional Requirements with Aspects: An Industrial Case Study“.
In:  QSIC 2007 Portland. pp. 5-14. (2007). \url{10.1109/QSIC.2007.4385475}

\bibitem{Parnas} Parnas, D.: On the criteria to be used in decomposing systems into modules.
In: Communications of the ACM. (1972)


\end{thebibliography}

\listoffigures

\listoftables

\end{document}          
