\documentclass[a4paper,10pt, bibliography=totocnumbered]{scrreprt}

\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}

\usepackage{graphicx}
\usepackage{pdfpages}
%\usepackage{subfig}
%\usepackage{microtype}
\usepackage{tabularx}
%\usepackage{amsmath, textcomp}

% Custom packages
\usepackage[numbers]{natbib}
\usepackage{ragged2e}
\usepackage{longtable}
%\usepackage{tikz}
%\usetikzlibrary{positioning}
%\usepackage{pdflscape}
%\usepackage{rotating}

%----------Begin Hausberger Packages-----------
%\usepackage{csquotes}
%\usepackage{float}
\usepackage{longtable}
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{
	frame=tb,
	language=Java,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
	morekeywords={UC, context, pre, @pre, post, and, or, not, implies, forall, exists},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	stringstyle=\color{mauve},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3
}
%----------End Hausberger Packages-----------

\usepackage{glossaries} 

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,        % color of internal links
%    citecolor=green,        % color of links to bibliography
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}


%% Title Page
\makeatletter
\renewcommand{\maketitle}{\begin{titlepage}
    \vskip 10\p@
    \hbox{
      \vrule depth 0.99\textheight
        \mbox{\hspace{2em}}
      \vtop{
        \vskip 10\p@
        \hspace{4pt}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@author \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \huge \bfseries \@title \par
        \end{flushleft}
        \begin{flushleft}
          \Large \bfseries \@subtitle \par
        \end{flushleft}
        \vskip 70\p@
        \begin{flushleft}
          \Large \@publishers \par
        \end{flushleft}
        \vskip 50\p@
        \begin{flushleft}
          \Large \@date \par
        \end{flushleft}
        }}
  \end{titlepage}
}
\makeatother

\author{Author 1, Author n}
\title{Title }
\subtitle{Technical Report}
\publishers{\textbf{Advisor University of Heidelberg}\\ Prof. Dr. Barbara Paech, Astrid Rohmann}
\date{mm dd, year}



% Deutsche Absaetze:
\parindent 0pt
\parskip 12pt

\textwidth145mm
\setlength{\oddsidemargin}{0.7cm}
\setlength{\topmargin}{-0.5cm}
\setlength{\textheight}{22.5cm}

\begin{document}
\maketitle

\include{./content/0-Abstract}

\tableofcontents

\input{./content/1-Introduction}
\input{./content/2-Chapter2}
\input{./content/3-Chapter3}
\input{./content/4-Chapter4}
\input{./content/10-Conclusion}
\input{./content/11-Glossary}

%% Bibliography
\bibliographystyle{plainnat}
%\bibliography{literature.bib}%Bibliography file name

\begin{thebibliography}{9}

\bibitem{KunChen2005} Chen, K, Zhang, W., Zhao, H.: An approach to constructing feature models based on requirements clustering.
In: 13th IEEE International Conference on Requirements Engineering (RE05). pp. 31-40. (2005)

\bibitem{RichtigesZitierenTUDresden} Institut für Geographie   
Lehrstuhl für Allgemeine Wirtschafts- und Sozialgeographie: An Hinweise zum wissenschaftlichen Arbeiten.
\url{http://www.geogr.uni-jena.de/fileadmin/Geoinformatik/Lehre/backup_05_2007/pdf-dokumente/Skript_WissArbeiten.pdf}

\bibitem{ClementineNebut2006} Nebut, C., Fleurey, F., Le Traon, Y., Jézéquel, J.-M.: Automatic Test Generation: A Use Case Driven Approach.
In: IEEE Transactions on Software Engineering (Volume: 32, Issue: 3, March 2006).
https://doi.org/10.1109/TSE.2006.22.

\bibitem{NajlaRaza2007} Raza, N., Nadeem, A., Iqbal, M. Z. Z.: An Automated Approach to System Testing based on Scenarios and Operations Contracts.
In: Seventh International Conference on Quality Software (QSIC 2007).
https://doi.org/10.1109/QSIC.2007.4385504.

\bibitem{FelixHausberger2020} Hausberger, F.: Research planning, research and mid-term presentation, \url{https://github.com/fidsusj/SWE-Seminar}, last accessed 2021/01/10.

\bibitem{MonalisaSarma2007} Sarma, M., Mall, R.: System Testing using UML Models.
In: 16th IEEE Asian Test Symposium (ATS 2007).
https://doi.org/10.1109/ATS.2007.102.

\bibitem{RosziatiIbrahim2007} Ibrahim, R., Saringat, M. Z., Ibrahim, N., Ismail, N.: An Automatic Tool for Generating Test Cases from the System's Requirements.
In: 7th IEEE International Conference on Computer and Information Technology (CIT 2007).
https://doi.org/10.1109/CIT.2007.116.

\bibitem{LizheChen2010} Chen, L., Li, Q.: Automated test case generation from use case: A model based approach.
In: 2010 3rd International Conference on Computer Science and Information Technology.
https://doi.org/10.1109/ICCSIT.2010.5563772.

\bibitem{XiaojingZhang2015} Zhang, X., Tanno, H.: Requirements document based test scenario generation for web application scenario testing.
In: 2015 IEEE Eighth International Conference on Software Testing, Verification and Validation Workshops (ICSTW).
https://doi.org/10.1109/ICSTW.2015.7107465.

\bibitem{LipingLi2008} Li, L., Miao, H.: An Approach to Modeling and Testing Web Applications Based on Use Cases.
In: 2008 International Symposium on Information Science and Engineering.
https://doi.org/10.1109/ISISE.2008.265.

\bibitem{YGKim1999} Kim, Y. G., Hong, H. S., Cho, S. M., Bae, D. H., Cha, S. D.: Test cases generation from UML state diagrams.
In: IEEE Proceedings - Software, Vol. 146, No. 4, pp. 187-192, Aug. 1999.
https://doi.org/10.1049/ip-sen:19990602.

\bibitem{ClementineNebut2003} Nebut, C., Fleurey, F., Le Traon, Y., Jézéquel, J.-M.: Requirements by Contracts allow Automated System Testing.
In: Proceedings of the 14th International Symposium on Software Reliability Engineering (ISSRE November 2003).
https://dl.acm.org/doi/10.5555/951952.952350.

\end{thebibliography}

\listoffigures

\listoftables

\end{document}          
